\bf Tuning parameter selection for a penalized estimator of species richness

### 2019-08-08 rre_manuscript/paper.tex
final numbers for Pasolli analysis

We also applied our method to estimate the species-level diversity of human host associated microbes.
\cite{pasolli2019extensive} assembled $c=4,930$ species-level genome bins (SGBs) using publicly available shotgun metagenomic data, but we expect that many SGBs were not observed due to undersampling and challenges in genome assembly. The frequency counts of each SGB are available at \cite[Table S4]{pasolli2019extensive}.

In this dataset $r=1$, and so it is not possible to sample split replicate frequency count tables. Therefore, only Methods 0 and Method 3 can be applied. With $\lambdagrid = \{0, 0.25, \ldots, 1100\}$ we found that Method 3 selected $\lambda = 913.5$. However, $\widehat{C}_{[3]} = 98600$

We found that $\widehat{C}_{[0]} = 420056$ with $(\hat{\alpha}, \hat{\delta}) = (0.00234, 0.00641).$

>>>>

We also applied our method to estimate the species-level diversity of human host associated microbes.
\cite{pasolli2019extensive} assembled $c=4,930$ species-level genome bins (SGBs) using publicly available shotgun metagenomic data, but we expect that many SGBs were not observed due to undersampling and challenges in genome assembly. The frequency counts of each SGB are available at \citet[Table S4]{pasolli2019extensive}.

In this dataset $r=1$, and so it is not possible to sample split replicate frequency count tables. Therefore, only Methods 0 and Method 3 can be applied. We found that $\widehat{C}_{[0]} = 420056$ with $(\hat{\alpha}, \hat{\delta}) = (0.00234, 0.00641).$ In contrast, $\widehat{C}_{[3]} = 163587$ with $\tilde{\lambda}_{[3]} = 905$ and $(\hat{\alpha}, \hat{\delta}) = (0.006045614, 0.006352191).$
% With $\lambdagrid = \{0, 0.25, \ldots, 1100\}$ we found that Method 3 selected $\lambda = 913.5$. However, $\widehat{C}_{[3]} = 98600$
% We found that $\widehat{C}_{[3]} = 163587$ with $\tilde{\lambda}_{[3]} = 905$ and $(\hat{\alpha}, \hat{\delta}) = (0.006045614, 0.006352191).$ % GOF = 11196564679

\amy{TODO: Discussion}
